\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-07-22 TilingProjectDraft/tilingProject.tex
--no-message

For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
\begin{equation}\begin{aligned}
	G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
\end{aligned}\end{equation}

@@

\section{Spectral functions and self-energies}

@@

From the knowledge of Greens function, one can write down self-energies using Dyson's equation \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\), where \(G^{(0)}\) is the non-interacting Greens function. The non-interacting model is simply a resonant-level model with the impurity level at zero energy. Following Dyson's equation, the \(k-\)space self-energy can be obtained from the \(k-\)space Greens functions:
\begin{equation}\begin{aligned}
	\label{self-energy1}
	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
\end{aligned}\end{equation}
where the superscript \((0)\) indicates that the corresponding term has to be calculated from the non-interacting auxiliary model.

@@

By using our tiling approach (eq.~\ref{k_Gf_siam}), the \(k-\)space Greens function of the lattice problem, at the critical point, can be shown to become independent of the momentum, through the vanishing of the momentum dependent contribution coming from \(\mathcal{G}_{dz}\):
\begin{equation}\begin{aligned}
	G_\text{H-H}(\vec k,\omega) = G_\text{loc}(\omega) + \frac{\xi_{\vec k}}{\lambda_{\vec k_0}^2\mathcal{W}}\mathcal{G}_{dz}(\omega) = G_\text{loc}(\omega)
\end{aligned}\end{equation}
This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish

>>>>

For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
\begin{equation}\begin{aligned}
	\label{greens_func_relation_near}
	G_\text{near-n}(t) \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
\end{aligned}\end{equation}
These relations can be easily carried over to frequency domain: 
\begin{equation}\begin{aligned}
	G_\text{loc}(\omega) = \int \mathrm{dt}~e^{-i\omega t} G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\int \mathrm{dt}~e^{-i\omega t} \mathcal{G}_{dd}(t) = \frac{1}{\lambda_{\vec k_0}^2} \mathcal{G}_{dd}(\omega)~.
\end{aligned}\end{equation}

@@

\section{\(k-\)space Greens functions and self-energies}

@@

A similar decomposition can be used to map the self-energies of the lattice model to those of the impurity model. We approximate the full \(k-\)space self-energy as
\begin{equation}\begin{aligned}
	\label{selfenergykspace}
	\Sigma(\vec k,\omega) \simeq \Sigma_\text{loc}(\omega) + \xi_{\vec k}\Sigma_\text{near-n}(\omega)~,
\end{aligned}\end{equation}
where \(\Sigma_\text{loc}(\omega) = \Sigma_\text{H-H}(\vec r=0,\omega)\) is the local self-energy and \(\Sigma_\text{near-n}(\omega) = \Sigma_\text{H-H}(\vec r=a, \omega)\) is the self-energy arising from processes that connect a site with its nearest neighbour. Following Dyson's equation, these self-energies can be written in terms of the real space Greens functions:
\begin{equation}\begin{aligned}
	\Sigma_\text{loc}(\omega) = \left( G_\text{loc}^{(0)} \right) ^{-1} - \left( G_\text{loc} \right) ^{-1} = \lambda_{\vec k_0}^2\left[\left( \mathcal{G}_{dd}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dd} \right) ^{-1}\right]~,
\end{aligned}\end{equation}
where \(G_\text{loc}^{(0)}\) and \(\mathcal{G}_{dd}^{(0)}\) are the local non-interacting Greens functions of the full model and the impurity model respectively, and we have used eq.~\ref{greens_func_relation}. In the same way, following eq.~\ref{greens_func_relation_near}, the nearest-neighbour self-energy can be written as
\begin{equation}\begin{aligned}
	\Sigma_\text{near-n}(\omega) = \mathcal{W}\lambda_{\vec k_0}^2\left[\left( \mathcal{G}_{dz}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dz} \right) ^{-1}\right]~,
\end{aligned}\end{equation}
where \(\mathcal{G}_{dz}^{(0)}\) is the nearest-neighbour non-interacting Greens functions of impurity model.

Substituting these in eq.~\ref{selfenergykspace} allows us to express the \(k-\)space self-energy in terms of auxiliary model objects:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = \lambda_{\vec k_0}^2\left[ \left( \mathcal{G}_{dd}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dd} \right) ^{-1} + \xi_{\vec k}\left( \mathcal{G}_{dz}^{(0)} \right) ^{-1} - \xi_{\vec k}\left( \mathcal{G}_{dz} \right) ^{-1} \right] = \lambda_{\vec k_0}^2\left[ \Sigma_{dd}(\omega) + \xi_{\vec k}\Sigma_{dz}(\omega) \right]~,
\end{aligned}\end{equation}
where \(\Sigma_{dd}\) and \(\Sigma_{dz}\) are the impurity and impurity-zeroth site self-energies of the impurity model.

@@

By using our tiling approach (eq.~\ref{k_Gf_siam}), the \(k-\)space Greens function of the lattice problem, at the critical point, can be shown to become independent of the momentum, through the vanishing of the momentum dependent contribution coming from \(\mathcal{G}_{dz}\):
\begin{equation}\begin{aligned}
	G_\text{H-H}(\vec k,\omega) = G_\text{loc}(\omega) + \frac{\xi_{\vec k}}{\lambda_{\vec k_0}^2\mathcal{W}}\mathcal{G}_{dz}(\omega) = G_\text{loc}(\omega)
\end{aligned}\end{equation}
This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish .
